Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-08-07 pirouette_supplement.tex
Add DOIs to code and data

All code is archived at 
\url{http://github.com/richelbilderbeek/pirouette_article},
with DOI \url{https://doi.org/12.3456/zenodo.1234567}.

>>>>

The pirouette code used for the examples 
is archived at DOI \url{https://doi.org/10.5281/zenodo.3969839}.
The pirouette examples (including intermediate data) are archived at 
DOI \url{https://doi.org/10.5281/zenodo.3970000}.
